Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-02-01 docs/msr.tex
tighten up authors (no effect)
description of categories ready

\author{
\IEEEauthorblockN{Dimitris Mitropoulos}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: dimitro@aueb.gr}
\and
\IEEEauthorblockN{Vassilios Karakoidas}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: bkarak@aueb.gr}\\
\and
\IEEEauthorblockN{Panos Louridas}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: louridas@aueb.gr}
\and
\IEEEauthorblockN{Diomidis Spinellis}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: dds@aueb.gr}
\and
\IEEEauthorblockN{Georgios Gousios}
\IEEEauthorblockA{Department of Software and Computer Technology\\
Delft University of Technology\\
Email: G.Gousios@tudelft.nl}
}

@@

\begin{figure*}
	\centering
	\includegraphics[scale=0.6]{version_count.pdf}
	\caption{Distribution of version count amongst project population}
	\label{fig:version-count}
\end{figure*}

@@

\begin{table}
\centering
\caption{Bug categorisation according to FindBugs}
\label{tbl:bug-categorisation}
\begin{tabular}{l p{15em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding mistakes resulting in code
that was probably not what the developer intended. \\
Experimental & \\
Internationalisation & Indicates the use of non-localized methods \\
Multi-Threaded Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usageallocation, usage 
of non-static classes \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Security & Contains two subcategories, namely: {\it Security} and {\it
Malicious Code}. Involves code that could lead to security breach. \\
\hline
\end{tabular}
\end{table}

>>>>

\author{
\IEEEauthorblockN{Dimitris Mitropoulos}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: dimitro@aueb.gr}\\
\and
\IEEEauthorblockN{Vassilios Karakoidas}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: bkarak@aueb.gr}\\
\and
\IEEEauthorblockN{Georgios Gousios}
\IEEEauthorblockA{Department of Software and Computer Technology\\
Delft University of Technology\\
Email: G.Gousios@tudelft.nl}\\
\and
\IEEEauthorblockN{Panos Louridas}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: louridas@aueb.gr}\\
\and
\IEEEauthorblockN{Diomidis Spinellis}
\IEEEauthorblockA{Department of Management Science and Technology\\
Athens University of Economics and Business\\
Email: dds@aueb.gr}}

@@

\begin{figure*}
	\centering
	\includegraphics[scale=0.6]{version_count.pdf}
	\caption{Distribution of version count among project population}
	\label{fig:version-count}
\end{figure*}

@@

\begin{table}
\centering
\caption{Bug categorisation according to FindBugs}
\label{tbl:bug-categorisation}
\begin{tabular}{l p{15em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding mistakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file \\
Internationalisation & Indicates the use of non-localized methods \\
Multi-Threaded Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usageallocation, usage 
of non-static classes \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Security & Contains two subcategories, namely: {\it Security} and {\it
Malicious Code}. Involves code that could lead to security breach. \\
\hline
\end{tabular}
\end{table}

\subsection{Analysis}
\label{sec:analysis}
